The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2013-06-18 script/en/script-en.tex
CT Script: Minor changes including the section about Shared Primes (currently only in English).

\vspace{30pt}
\begin{itemize}
  \item The source code of the Sage samples in this script is delivered as
        Sage program files within the CrypTool-1 setup program.
        All samples within one chapter are collected in one file.
        After installing CrypTool 1 \index{CrypTool 1} you find
        the Sage samples within the subdirectory \verb#sage# within the CrypTool-1
        directory:\\
        - SAGE-Samples-in-Chap01.sage \\
        - SAGE-Samples-in-Chap02.sage \\
        - SAGE-Samples-in-Chap03.sage \\
        - SAGE-Samples-in-Chap04.sage
  \item All samples have been tested with Sage Version 5.3 (Release Date 2012-09-08).
\end{itemize}

>>>>

\vspace{30pt}
\begin{itemize}
  \item The source code of the Sage samples in this script is delivered as
        Sage program files within the CrypTool-1 setup program.
        All samples within one chapter are collected in one file.
        After installing CrypTool 1 \index{CrypTool 1} you find
        the Sage samples within the subdirectory \verb#sage# in the
        following 4 files:\\
        - SAGE-Samples-in-Chap01.sage \\
        - SAGE-Samples-in-Chap02.sage \\
        - SAGE-Samples-in-Chap03.sage \\
        - SAGE-Samples-in-Chap04.sage
  \item All samples have been tested with Sage Version 5.3 (Release Date 2012-09-08).
\end{itemize}
